%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------

\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}

%---------------------------------------------------------

  \cventry
    {A2R Statutory \& Tax Project Lead} % Job title
    {Syngenta} % Organization
    {Budapest, Hungary} % Location
    {July 2023 - Present} % Date(s)
    {I lead projects related to statutory accounting, reporting, and tax processes in the EMEA region, where I am responsible for:} % Tagline
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Support the implementation of new business models, mergers and integrations while adhering to applicable corporate frameworks.}
        \item {Actively seek process improvements and implement corrective actions in consultation with the EAME A2R Head.}
        \item {Ensure automation is prioritized when building business cases to decide if investment in new A2R Statutory and Tax solutions is required.}
        \item {Leverage technology to drive efficient and effective processes and support the team in digital transformation, process improvement and automation.}
        \item {Foster collaboration with other regions to share best practices and drive effective end-to-end finance operations activities.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Statutory \& Direct Tax Senior Accountant} % Job title
    {Syngenta} % Organization
    {Budapest, Hungary} % Location
    {February 2021 - June 2023} % Date(s)
    {My responsibilities covered the following areas related to Syngenta's Iberia portfolio's statutory and corporate tax matters:} % Tagline
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead and ensure that statutory financial statements/tax filings are prepared for all entities.}
        \item {Ensure the Group Transfer Pricing framework is implemented and followed, providing country-specific regulations feedback to Group Reporting/Group Tax teams.}
        \item {Ensure that the statutory changes are reflected in Group Reporting.}
        \item {Facilitate external audits and coordinate third-party financial service providers.}
        \item {Continuously monitor internal and external risks that may arise and address any regulatory changes.}
      \end{cvitems}
  }

%---------------------------------------------------------

  \cventry
    {Netherlands Direct Tax \& Reporting Junior Manager} % Job title
    {Diageo} % Organization
    {Budapest, Hungary} % Location
    {January 2020 - January 2021} % Date(s)
    {In this role, I was responsible for the following areas in relation to the corporate tax matters of Diageo's Dutch portfolio:} % Tagline
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Preparation and management of corporate tax compliance work, including fiscal unions.}
        \item {Calculation of corporate income tax and preparation of tax notes to financial statements.}
        \item {Review monthly cash tax and forecast ETR.}
        \item {Manage tax payments and provisional assessments.}
        \item {Monitor overall tax position and assist with annual operating plan, group reporting, prior year adjustments, and ad-hoc tax-related inquiries.}
      \end{cvitems}
  }

%---------------------------------------------------------

  \cventry
    {Statutory Compliance Supervisor — Corporate Tax} % Job title
    {Diageo} % Organization
    {Budapest, Hungary} % Location
    {February 2018 - December 2019} % Date(s)
    {This position gave me a broader view of corporate tax compliance work, such as:} % Tagline
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Review tax compliance materials prepared by senior team members.}
        \item {Prepare tax compliance work for the Dutch portfolio.}
        \item {Manage the entire tax compliance cycle for assigned companies.}
        \item {Review transfer pricing margin check files and communicate deadlines to markets.}
        \item {Assist the Tax Manager with team management and activity allocation, scope expansion and knowledge retention projects, and compliance-related requests.}
      \end{cvitems}
  }

%---------------------------------------------------------

  \cventry
    {Direct Tax Accountant} % Job title
    {AIG} % Organization
    {Budapest, Hungary} % Location
    {May 2016 - December 2017} % Date(s)
    {As a member of the EMEA Tax team based in the Budapest Accounting Center, I was involved in:} % Tagline
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supporting the quarterly US GAAP and IFRS tax reporting process, including preparing tax provisions, reconciling accounts to tax provision reports, and assisting in the preparation of SOX documentation.}
        \item {Supporting the Finance Center in its day-to-day tax activities (technical issues, tax opportunities, compliance, deferred taxes, transfer pricing, tax balance sheet, and tax calculations).}
        \item {Act as a liaison between local finance and regional tax teams.}
        \item {Successfully transferred all Finance Center-related tax activities and knowledge to India.}
      \end{cvitems}
  }

%---------------------------------------------------------

  \cventry
    {Senior Tax / Forex / Pension Analyst} % Job title
    {ExxonMobil} % Organization
    {Budapest, Hungary} % Location
    {September 2014 - May 2016} % Date(s)
    {In this role, I worked with subsidiaries in the EMEA region and was responsible for:} % Tagline
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Executing the month-end, quarter-end, and year-end closing processes.}
        \item {Calculating current and deferred income tax provisions in accordance with FAS 109.}
        \item {Calculation of net periodic pension cost under FAS 87 and pension liability adjustments under FAS 158.}
        \item {Reconciliation of effective tax rates to statutory tax rates.}
        \item {Analyze movements in current and noncurrent deferred tax balances.}
        \item {Review of foreign exchange revaluation processes in SAP - including analysis of fluctuations.}
      \end{cvitems}
  }

%---------------------------------------------------------

\cventry
{Accountant} % Job title
{Budapest University of Technology \& Economics} % Organization
{Budapest, Hungary} % Location
{January 2013 - September 2014} % Date(s)
{As a member of the accounting group, my responsibilities included:} % Tagline
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Issuing foreign currency invoices in accordance with sales contracts on an institutional level.}
    \item {Working as part of a team to prepare the balance sheet, income statement, and other periodic and ad hoc reports.}
    \item {Posting general ledger entries of service charges between business units and those required by my other responsibilities.}
    \item {Review and return vendor and customer statements.}
    \item {Ensure business units are aware of any unresolved/unaligned revenue, outstanding invoices, and their VAT implications.}
  \end{cvitems}
}

%---------------------------------------------------------

\end{cventries}
